ChIP-exo: High Resolution Identification of Protein-DNA Binding Events and Quality Control

### 2015-11-03 rmarkdown/chip_exo_paper.Rnw
run several cases of condition and saturation analyiss and updated background part of paper

While the number of produced ChIP-exo data keeps increasing,
characteristicos of ChIP-exo data and optimal strategies for
experimental design and analysis of ChIP-exo data are not fully
investigated yet, including issues of sequence biases inherent to
ChIP-exo data, choice of optimal statistical methods, and
determination of optimal sequencing deoth. However, currently, the
number of available ChIP-exo data is still limited and their
sequencing depths are still insufficient for such investigation. To
address this limitation we gathered ChIP exo data from diverse
organisms: CTCF factor in human \cite{exo1}; ER factor in human and
FoxA1 factor in mouse from \cite{exo_illumnina}; and generated
$\sigma^{70}$ factor in Escherichia coli (E. Coli) under aerobic ($ +
O_2$) condition, and treated by rifampicin by 0 and 20 minutes.

>>>>

While the number of produced ChIP-exo data keeps increasing,
characteristicos of ChIP-exo data and optimal strategies for
experimental design and analysis of ChIP-exo data are not fully
investigated yet, including issues of sequence biases inherent to
ChIP-exo data, choice of optimal statistical methods, and
determination of optimal sequencing deoth. However, currently, the
number of available ChIP-exo data is still limited and their
sequencing depths are still insufficient for such investigation. To
address this limitation we gathered ChIP exo data from diverse
organisms: CTCF factor in human \cite{exo1}; ER factor in human and
FoxA1 factor in mouse from \cite{exoillumina}; and generated
$\sigma^{70}$ factor in Escherichia coli (E. Coli) under aerobic ($ +
O_2$) condition, and treated by rifampicin by 0 and 20 minutes.

In order to archieve potential benefits of ChIP exo on protein binding
site identification, it is critical to understand which are the
important characteristics of ChIP exo data and to use algorithms that
could fully utilize information available in ChIP exo data. Rhee and
Pugh \cite{exo1} discussed that reads in the forward and reverse
strand might construct peak apirs around bound protein, of which
heights were implicitly assumed to be symmetric. Hence, they used the
``peak pair method'' taht preducts the midpoint of two modes of pak
pairs as potential binding site. Apex, a recetly developed ChIP-exo
data analysis method, is also based on this peak pair
assumption. However, appropriatness of such assumption was not fully
evaluated in the literature yet. Furthermore, it is still unknown
which factors could affect protein binding site ientification using
ChIP exo data. In order to address this problem, we investigated
various aspects of ChIP exo data by contrasting them with their
respective ChIP Seq experiments.
